Phylodynamic inference of contact network parameters through approximate Bayesian computation

### 2016-06-02 doc/thesis/methods_results.Rnw
Added intro section to chapter 2

{\color{blue}\uline{
This chapter is organized as follows. One section is devoted to each of our
three research aims: the development of a method for inference of contact
network parameters from transmission trees} (\cref{sec:netabc}), \uline{the
investigation of the \acrlong{BA} network model using simulated data
}(\cref{sec:ba}), \uline{ and the application of the method to real-world
\gls{HIV} epidemics }(\cref{sec:hiv}). \uline{Each of these sections contains a
description of the methods used and, in the case of the latter two objectives,
the results of the experiments. The fourth and final section of the chapter
}(\cref{sec:disc}) \uline{contains a unified discussion of all three
objectives. }}

>>>>

{\color{blue}\uline{ In this chapter, we will address the three research aims
of this thesis introduced in} \cref{sec:obj}. \uline{First, in}
\cref{sec:netabc}, \uline{we describe \software{netabc}, a computer program
that implements an \acrlong{ABC}-based algorithm to fit contact network models
to phylogenetic data. We also provide a justification for the use of \gls{ABC}
for this problem by arguing that the likelihood functions required to fit these
models by more conventional means are likely to be computationally intractable.
Second, in} \cref{sec:ba}, \uline{we perform a simulation study to investigate
the \acrlong{BA} network model, which uses a preferential attachment mechanism
to generate networks with the power law degree distributions observed in real
world social and sexual networks. We progress through two exploratory analyses
testing the identifiability of the model's parameters, and conclude by testing
\software{netabc}'s ability to recover the parameters from simulated
transmission trees. Third, in} \cref{sec:hiv}, \uline{we apply
\software{netabc} to fit the \gls{BA} model to six real world \gls{HIV}
datasets, with the understanding of the model parameters' identifiability
gained through the simulation experiments. We conclude the chapter with a
unified discussion of the three research aims, including interpretation of the
results of both the simulated and real data experiments, as well as an
examination of the limitations of our approach and opportunities for future
investigation. }}
